Cross Validation Approaches for Penalized Cox Regression

### 2019-04-17 main.tex
elasticnet for shedden data

\par All of the cross-validation approaches described in Section~\ref{Sec:methods} use the Cox partial likelihood, in one way or another, as the criterion upon which model selection is based.  In this section, we compare these likelihood-based approaches against an alternative approach of cross validation using concordance, also known as the cross-validated AUC (CV-AUC).  This is a widely used approach to cross-validation with time-to-event outcomes, particularly for machine learning models that are not likelihood-based \citep{Subramanian2011,Simon2011a}. This approach typically proceeds by constructing cross-validated linear predictors, as in Section~\ref{Sec:linear-predictor}, but then using those predictors to calculate concordance as opposed to partial likelihood.

\par We conducted simulations in both low dimensional ($p = 50$) and high dimensional ($p = 1000$) settings, varying the signal in the data \note{as in Section 3.1?} \note{is $n=100$ here?}. Results of the simulations are illustrated in Figure~\ref{Fig:cvauc}.  We used the linear predictor approach (CV-LP) here as the representative approach for likelihood-based cross-validation.

Several observations can be drawn from Figure~\ref{5}.  First, likelihood-based CV tends to select more accurate models, as judged by both mean squared error and Brier score.  Second, likelihood-based CV is also more stable than the AUC-based CV, in the sense that it tends to select a narrower range of models, with more consistent performance, than CV-AUC.  Lastly, CV-AUC is consistently more liberal than likelihood-based CV, selecting models with smaller values of the regularization parameter $\lam$, and therefore preferring models with larger coefficient values and more nonzero coefficients.

>>>>

\par All of the cross-validation approaches described in Section~\ref{Sec:methods} use the Cox partial likelihood, in one way or another, as the criterion upon which model selection is based.  In this section, we compare these likelihood-based approaches against an alternative approach of cross validation using concordance, also known as the cross-validated C Index.  This is a widely used approach for conducting cross-validation with time-to-event outcomes, particularly for machine learning models \citep{Subramanian2011,Simon2011a}. This approach typically proceeds by constructing cross-validated linear predictors, as in Section~\ref{Sec:linear-predictor}, but then using those predictors to calculate concordance as opposed to partial likelihood.

\par We conducted simulations in both low dimensional ($p = 50$, $n = 150$) and high dimensional ($p = 1000$, $n = 120$) settings. For each of the scenario, we generated data from a spectrum of signal strength as in Section~\ref{Sec:accuracy}. Results of the simulations are illustrated in Figure~\ref{Fig:cvauc}.  We used the linear predictor approach (CV-LP) here as the representative approach for likelihood-based cross-validation.

Several observations can be drawn from Figure~\ref{Fig:cvauc}. First, likelihood-based CV tends to select more accurate models, as judged by both mean squared error and Brier score.  Second, likelihood-based CV is also more stable than the AUC-based CV, in the sense that it tends to select a narrower range of models, with more consistent performance, than CV-AUC.  Lastly, CV-AUC is consistently more liberal than likelihood-based CV, selecting models with smaller values of the regularization parameter $\lam$, and therefore preferring models with larger coefficient values and more nonzero coefficients.

\bnote{(END)}
